### 2021-02-02 research project/sections/Analysis_of_results.tex
rp

@@

To better show the trend in the data collected, see below the decimal places compared 
to the time taken per method. The blue markers and line of best-fit 
respresent the results received from Viète's method while the red represent those 
from Madhava's method. \\

@@

Include Decimal places vs Iterations

@@

The results gathered from this experiment show linear relationship between the amount of decimal 
places approximated and the time required for this approximation. The two lines of best fit for 
the two methods show similarities but also differences. It can be firstly noted that Madhava's 
method is faster than the other until the decimal 20, when the two best fit lines diverge. This 
can be explained as due to the convergence rates of the two methods, which can be seen in (Figure 3) 
\ref{fig:comparaison}. In the beginning of this curve representing the convergence of Viète's method, 
it can be seen that it does not follow an \textit{alternating} method, like the one formulated by 
Madhava. Madhava's method is what is called an alternating series, in this case one that converges 
to the value $\pi$, and as such it is closer to the correct value of $\pi$ at lower decimal values 
and gradually takes longer and longer than Viète's method, which is an infinite product. This difference 
in speeds can be attributed to the fact that

>>>>

\pgfplotstableread{
    X Y
    5 10
    10 17
    15 27
    20 35
    25 42
    30 51
    35 59
    40 67
    45 76
    50 84
    55 92
    60 101
}\vietetableiter

\pgfplotstableread{
    X Y
    5 9
    10 20
    15 29
    20 41
    25 50
    30 61
    35 71
    40 82
    45 91
    50 102
    55 112
    60 123
}\madhavatableiter

@@

Shown below is a graph demonstrating the correlation between the decimal places approximated 
and the amount of iterations needed for this specific decimal milestone. The blue markers and 
line of best-fit respresent the results received from Viète's method while the red represent those 
from Madhava's method. \\

\begin{tikzpicture}[scale=1.1]
    \begin{axis}[
        title={Comparing the iterations needed for approximating the value of $\pi$},
        xlabel={Decimal places},
        ylabel={Iterations},
        xmin=0, xmax=60,
        ymin=0, ymax=130,
        ytick={0,10,20,30,40,50,60,70,80,90,100,110,120,130},
        xtick={0,10,20,30,40,50,60},
        legend pos=north west,
        ymajorgrids=true,
        grid style=dashed,
        scale=1.2
    ]

    \addplot[
        only marks,
        color=blue,
        mark=*,
        ] table {\vietetableiter};
        \legend{Viète's method}

    \addplot [thin, blue] table[
        y={create col/linear regression={y=Y}}
    ] % compute a linear regression from the input table
    {\vietetableiter};
    \addlegendentry{best fit line}

    \addplot[
        only marks,
        color=red,
        mark=*,
        ] table {\madhavatableiter};
        \addlegendentry{Madhava's method}

    \addplot [thin, red] table[
        y={create col/linear regression={y=Y}}
    ] % compute a linear regression from the input table
    {\madhavatableiter};
    \addlegendentry{best fit line}

To show the trend in the time data collected, see below the decimal places compared 
to the time taken per method. The color coding here is relevant to the one aforementioned. \\

@@

@@

The results gathered from this experiment show linear relationship between the amount of decimal 
places approximated and the time required for this approximation, as well as between the decimal places 
and the amount of iterations needed. The two lines of best fit for the two methods show 
similarities but also differences.

Where decimal places and iterations are compared, there is a clear difference between the two 
methods: Madhava's method indeed takes more iterations to converge to a specific decimal of 
the value $\pi$. However, in the second graph comparing time, it can be noted that Madhava's 
method is marginally faster until the decimal 20, when the two methods diverge. It could be 
assumed that this occurrence is due to differences between the types of the two methods. Madhava's 
method is what is called an alternating series, due to its nature of alternating between values in order 
to converge to a specific value, in this case $\pi$, while Viète's method is an infinite product. The 
difference between these two methods is underlined in (Figure 3) \ref{fig:comparaison}. It can be 
deduced that at lower decimal values Madhava's method is faster as Viète's method's approximation 
accuracy increases in what looks like an exponential fashion.

\textit{More info to be added}
